The Astropy Project

### 2017-12-06 main.tex
address reviews

@@

\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate. This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.

@@

\subsubsection{Creating New Models}

New model classes can be created in two ways:
\begin{enumerate}
   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
\end{enumerate}

@@

\acknowledgments The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students ofter turn into long-term contributors. We also
thank NumFOCUS and the Python Software Foundation for financial
support for various needs. Within the academic community, we thank
institutions that make it possible that astronomers and programmers on
their staff can contribute (part of) their time to the development of
\astropy projects. Furthermore, the \astropy packages would not exisit
in their current form without a number of webservices for code
hosting, continuous integration, and documentation; in particular,
\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
Read the Docs.  \astropypkg integrates with the SIMBAD database,
operated at CDS, Strasbourg, France.

>>>>

This article is not intended as an introduction to \astropypkg, nor does it replace the \astropypkg documentation. Instead, it describes the way the \astropy community is organized and the current state of the \astropypkg package.

@@

\package{astropy.modeling} provides an efficient way to set up the same type of model with many different sets of parameter values.
This creates a model set that can be efficiently evaluated. For example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.

@@

\subsubsection{Creating New Models}
If arithmetic combinations of existing models is not sufficient, new model classes can be defined in different ways. The \package{astropy.modeling} provides tools to turn a simple function into a full-featured model, but it also allows extending the build-in model class with arbitrary code.

@@

\acknowledgments

Who to thank?  numfocus, GSOC, Python Software Foundation

We thank the many web services that make developing and maintaining this package
feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
